---
title: "Final_ES193DS"
author: "Daniela Lopez"
format: html
editor: visual
output: 
  html_document: 
    toc: true
    toc_float: true
---

```{r}
library(tidyverse)
library(janitor)
library(here)
library(ggeffects)
library(flextable)
library(readxl)
library(MuMIn)
library(scales)
```

## Problem 1 

#### a. transparent statistical methods

In part 1, they used Pearson's correlation as they were measuring the strength and directions of the two variables being distance from headwater and total nitrogen load. In part 2, they used ANOVA as they determined that there is no difference in the means of two or more groups, those being urban land, atmospheric deposition, fertilizer, wastewater treatment, and grassland.

#### b. more information needed

Two additional tests or pieces of information that should be included could be the post-hoc test as it determines which sources have different means and effect size as it measures the strength of realtionships between the groups or nitrogen loads

#### c. suggestions for rewrtting

biological: For part 1, Sites that were further from the headwater had a higher annual nitrogen load suggesting that the nitrogen accumulates along the river.

statistical: Pearson correlation test, r = (), p = 0.03, α = 0.05, and df().

biological : For part 2, The nitrogen load averages were very different among nitrogen sources with some sources playing a more significant contribution than others.

statistical: one way ANOVA, F(), p= 0.02, α = 0.05, and df()

## Problem 2 

#### a. Cleaning and summarizing

```{r}
stt_clean <- read_csv("data/sstdata.csv") |> 
  mutate(data= ymd(date)) |>
  mutate(year= year(data),
         month = month(data))
```

#### b.  Visualize the data

## Problem 3 

#### a. Response variable

#### b. Purpose of study

#### c. Difference in "seasons"

#### d. Table of models 

#### e. Run the models

#### f. Check the diagnostics

#### g. Select the best model

#### h. Visualize the model prediction

#### i. Write caption for figure

#### j. Calculate model predictions

#### k. Interpret results

## Problem 4 

#### a. Comparing Visualizations 
