---
title: "Final_ES193DS"
author: "Daniela Lopez"
date: 11-06-25
format: html
editor: visual
output: 
  html_document: 
    toc: true
    toc_float: true
---

```{r}
library(tidyverse)
library(janitor)
library(here)
library(ggeffects)
library(flextable)
library(readxl)
library(MuMIn)
library(scales)
```

## Problem 1

#### a. transparent statistical methods

In part 1, they used Pearson's correlation as they were measuring the strength and directions of the two variables being distance from headwater and total nitrogen load. In part 2, they used ANOVA as they determined that there is no difference in the means of two or more groups, those being urban land, atmospheric deposition, fertilizer, wastewater treatment, and grassland.

#### b. more information needed

Two additional tests or pieces of information that should be included could be the post-hoc test as it determines which sources have different means and effect size as it measures the strength of realtionships between the groups or nitrogen loads

#### c. suggestions for rewrtting

biological: For part 1, Sites that were further from the headwater had a higher annual nitrogen load suggesting that the nitrogen accumulates along the river.

statistical: Pearson correlation test, r = (), p = 0.03, α = 0.05, and df().

biological : For part 2, The nitrogen load averages were very different among nitrogen sources with some sources playing a more significant contribution than others.

statistical: one way ANOVA, F(), p= 0.02, α = 0.05, and df()

## Problem 2

#### a. Cleaning and summarizing

```{r}
sst_clean <- read_csv("data/sstdata.csv") |> #load data and rename
  mutate(data= ymd(date)) |>
  mutate(year= year(data),
         month = month(data, label = TRUE)) |> 
  filter(year >= 2018, year <= 2023) |>#only keeps rows between those years
group_by(site, year, month) |> 
  summarise( 
    mean_monthly_sst = mean(temp, na.rm = TRUE))|> 
  mutate(month= factor (month, ordered= TRUE))

sst_clean |> 
  slice_sample(n=5) #get 5 random rows


```

#### b. Visualize the data

## Problem 3

#### a. Response variable

In this data set, a 1 represents a swift parrot in the nest box while a 0 represents absence of swift parrot in nest box.

#### b. Purpose of study

Swift parrots are a threatened species in this study while the other two species are considered invasive. The study uses the absence of the swift parrot to tell if the habitat restoration is working.

#### c. Difference in "seasons"

The study represents data from the summer breeding "seasons " of 2016 and 2019. These summers were when swift birds bred and during the interval, parrots were absent.

#### d. Table of models

```{r}
occ <- read.csv("occdist.csv") |>#load data
rename_with(make.names) |>  
mutate(season = as.factor(season))     # Make season a factor

# Fit the models
model1 <- glm(sp ~ 1, data = occ, family = binomial)                        # Null model
model2 <- glm(sp ~ season + edge.distance, data = occ, family = binomial)  # Full model
model3 <- glm(sp ~ season, data = occ, family = binomial)                  #only season
model4 <- glm(sp ~ edge.distance, data = occ, family = binomial)           # only distance 

```

#### e. Run the models

#### f. Check the diagnostics

#### g. Select the best model

#### h. Visualize the model prediction

#### i. Write caption for figure

#### j. Calculate model predictions

#### k. Interpret results

## Problem 4

#### a. Comparing Visualizations

The visualizations were extremely different from each other. My exploratory visualization was almost like a non-linear step function with yes work day on the right and non-work day on the left with the ounces of water consumed on the y-axis. My affective visualization was a graph over time on my water intake and the sharp turns were non work days compared to work days. The similarities seen on my visuals were the water intake ounces on the y-axis and both graphs. Both visualizations show me drinking a lot more water while I am at work. During workshop nine I was told my visual wasn't as clear but I was not sure how to change it. I made a box plot which I liked a lot more but the graph over time seemed to have a better fit although I was also told they had a hard time figuring out which was non work days vs work days in workshop 10.
